### 2020-03-30 papers.tex
papers.tex: Number the number review's page correctly
Add Ben's paper
Revert "papers.tex: Embiggen track title for better flow"
This reverts commit 812396bd1d7cefc4c5076b42a431163b8febd081, which did not play well with the front
table of contents!
Assign COVID-19 review
Update Ben's keywords
papers.tex: Try another trick to make the conspiracy theories track name fit

\addtrack
	{}{SIGBOVIK}
\addpaper
	{A thorough investigation of the degree to which the COVID-19 pandemic has enabled subpar-quality papers to make it into the proceedings of SIGBOVIK, by reducing the supply of authors willing to invest the necessary effort to produce high-quality papers}
	{Shalin Shah}
	{Keywords: COVID-19, SIGBOVIK, lazy, quality, sadness, big Oof}
	{SIGBOVIK_2020_paper_36}
	{0cm}
	{}
\addpaper
	{Is this the longest Chess game?}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, chesses, chessing, G.\@ K.\@ Chesterton}
	{SIGBOVIK_2020_paper_28}
	{0cm}
	{}
\addpaper
	{Optimizing the SIGBOVIK 2018 speedrun}
	{leo60228}
	{Keywords: speedrun, SIGBOVIK, pathfinding, DFS, Rust}
	{SIGBOVIK_2020_paper_20}
	{0cm}
	{}
\addpaper
	{Retraction of a boring follow-up paper to ``Which ITG stepcharts are turniest?'' titled, ``Which ITG stepcharts are crossoveriest and/or footswitchiest?''}
	{Ben Blum}
	{Keywords: groove, in, retraction, the}
	{SIGBOVIK_2020_paper_18}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_9}{0cm}

@@

\addtrack
	{}{Security}
\addpaper
	{Determining the laziest way to force other people to generate random numbers for us using IoT vulnerabilities}
	{mathmasterzach, StarChar}
	{Keywords: babies, information theory, randomness, entropy, April fools, hacking, the law, coffee shops, smart-toasters}
	{SIGBOVIK_2020_paper_4}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_6}{0cm}
\addpaper
	{Putting the ceremony in ``authentication ceremony''}
	{Camille Cobb, Sruti Bhagavatula}
	{Keyword: authentication, ceremony, fun, security, weddings}
	{SIGBOVIK_2020_paper_23}
	{0cm}
	{}

@@

\addtrack
	{}{Education}
\addpaper
	{A disproof of the Theorem of Triviality}
	{Arul Kolla, August Deer, Ethan Kogan}
	{Keywords: theorem of triviality, theorem, meta problems, meta, math i guess}
	{SIGBOVIK_2020_paper_5}
	{0cm}
	{}
\addpaper
	{Visualizing player engagement with virtual spaces using GIS}
	{Frederick Chan}
	{Keywords: geographic information systems, virtual spaces, video games, video game anthropology}
	{SIGBOVIK_2020_paper_3}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_2}{0cm}

@@

\addtrack
	{}{\LARGE The SIGBOVIK 2020 Field Guide to Conspiracy Theories}
\addpaper
	{Faking ancient computer science:\@ A special SIGBOVIK tutorial}
	{Roxanne van der Pol, Brian van der Bijl, Diederik M.\@ Roijers}
	{Keywords: ancient computer science, aliens, conspiracy theories, Triangle of Conspiracy Succession, probability, Arcaicam Esperantom, random number generator, pseudo-science}
	{SIGBOVIK_2020_paper_7}
	{0cm}
	{}
\addpaper
	{MORSE OF COURSE:\@ Paper reveals time dimension wasted}
	{Dougal Pugson}
	{Keywords: Morse code, performance, Bash, protocols}
	{SIGBOVIK_2020_paper_26}
	{0cm}
	{}
\addpaper
	{The Pacman effect and the Disc-Sphere Duality}
	{Francisco Ferreira, Fulvio Gesmundo, Lorenzo Gheri, Pietro Gheri, Riccardo Pietracaprina, Fangyi Zhou}
	{Keywords: Pacman, peace, Earth, flat, round, disc, sphere}
	{SIGBOVIK_2020_paper_37}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_4}{0cm}

>>>>

\addtrack
	{}{SIGBOVIK}
\addpaper
	{A thorough investigation of the degree to which the COVID-19 pandemic has enabled subpar-quality papers to make it into the proceedings of SIGBOVIK, by reducing the supply of authors willing to invest the necessary effort to produce high-quality papers}
	{Shalin Shah}
	{Keywords: COVID-19, SIGBOVIK, lazy, quality, sadness, big Oof}
	{SIGBOVIK_2020_paper_36}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_13}{0cm}
\addpaper
	{Is this the longest Chess game?}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, chesses, chessing, G.\@ K.\@ Chesterton}
	{SIGBOVIK_2020_paper_28}
	{0cm}
	{}
\addpaper
	{Optimizing the SIGBOVIK 2018 speedrun}
	{leo60228}
	{Keywords: speedrun, SIGBOVIK, pathfinding, DFS, Rust}
	{SIGBOVIK_2020_paper_20}
	{0cm}
	{}
\addpaper
	{Retraction of a boring follow-up paper to ``Which ITG stepcharts are turniest?'' titled, ``Which ITG stepcharts are crossoveriest and/or footswitchiest?''}
	{Ben Blum}
	{Keywords: groove, in, retraction, the}
	{SIGBOVIK_2020_paper_18}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_9}{0cm}

@@

\addtrack
	{}{Security}
\addpaper
	{Determining the laziest way to force other people to generate random numbers for us using IoT vulnerabilities}
	{mathmasterzach, StarChar}
	{Keywords: babies, information theory, randomness, entropy, April fools, hacking, the law, coffee shops, smart-toasters}
	{SIGBOVIK_2020_paper_4}
	{0cm}
	{}
\newcounter{egap}
\setcounter{egap}{\thepage}
\setcounter{page}{1}
\addreview{SIGBOVIK_2020_review_6}{0cm}
\setcounter{page}{\theegap}
\stepcounter{page}
\addpaper
	{Putting the ceremony in ``authentication ceremony''}
	{Camille Cobb, Sruti Bhagavatula}
	{Keyword: authentication, ceremony, fun, security, weddings}
	{SIGBOVIK_2020_paper_23}
	{0cm}
	{}

@@

\addtrack
	{}{Education}
\addpaper
	{A disproof of the Theorem of Triviality}
	{Arul Kolla, August Deer, Ethan Kogan}
	{Keywords: theorem of triviality, theorem, meta problems, meta, math i guess}
	{SIGBOVIK_2020_paper_5}
	{0cm}
	{}
\addpaper
	{Visualizing player engagement with virtual spaces using GIS}
	{Frederick Chan}
	{Keywords: geographic information systems, virtual spaces, video games, video game anthropology}
	{SIGBOVIK_2020_paper_3}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_2}{0cm}
\addpaper
	{How to \texttt{git bisect} when your test suite is having a bad day}
	{ben blum}
	{Keywords: pdflatex, cdflatex}
	{SIGBOVIK_2020_paper_39}
	{0cm}
	{}

@@

\addtrack
	{}{\textnormal{\normalsize The} SIGBOVIK 2020 Field Guide \textnormal{\normalsize to} Conspiracy Theories}
\addpaper
	{Faking ancient computer science:\@ A special SIGBOVIK tutorial}
	{Roxanne van der Pol, Brian van der Bijl, Diederik M.\@ Roijers}
	{Keywords: ancient computer science, aliens, conspiracy theories, Triangle of Conspiracy Succession, probability, Arcaicam Esperantom, random number generator, pseudo-science}
	{SIGBOVIK_2020_paper_7}
	{0cm}
	{}
\addpaper
	{MORSE OF COURSE:\@ Paper reveals time dimension wasted}
	{Dougal Pugson}
	{Keywords: Morse code, performance, Bash, protocols}
	{SIGBOVIK_2020_paper_26}
	{0cm}
	{}
\addpaper
	{The Pacman effect and the Disc-Sphere Duality}
	{Francisco Ferreira, Fulvio Gesmundo, Lorenzo Gheri, Pietro Gheri, Riccardo Pietracaprina, Fangyi Zhou}
	{Keywords: Pacman, peace, Earth, flat, round, disc, sphere}
	{SIGBOVIK_2020_paper_37}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_4}{0cm}
